Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-29 EMNLP-demo-paper/conclusion.tex
minor fix
update pixel bar layout scheme

We design the individual components with versatility in mind. Due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available models.
%
In the future, we plan to expand the visualization component further to handle tasks such neural machine translation and more.

>>>>

We design the individual components with versatility in mind. However, due to a large number of variants of attention networks, it is hard to ensure the current interface is compatible with all the available configurations.
%
In the future, we plan to improve the flexibility of the attention interface and expand the visualization component further to handle tasks such neural machine translation and more.

### 2018-05-29 EMNLP-demo-paper/relatedWorks.tex
update pixel bar layout scheme

\section{Related Works}
Due to the increasing demand for model interpretability, many previous works have been proposed for making sense NLP models by examining individual predictions as well as the model mechanism as a whole. 
%
In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based text representation is investigated by utilizing instance-level attribution techniques originated from the vision community, i.e., \cite{ZeilerFergus2014}. 
%
In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.

>>>>

\section{Related Works}
Due to the increasing demand for model interpretability, many previous works have been proposed for making sense of NLP models by examining individual predictions as well as the model mechanism as a whole. 
%
In the recent work~\cite{LiChenHovy2015}, the composability of the vector-based text representation is investigated by utilizing instance-level attribution techniques originated from the vision community, i.e., \cite{ZeilerFergus2014}. 
%
In the representation erasure work~\cite{li2016understanding}, the authors explain the neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.
